
\begin{frame}\section{Best Practices}
\begin{center}\textbf{\huge Best Practices}\end{center}
\end{frame}


\begin{frame}\begin{center}
	\textbf{Reference}\\\vspace{0.3cm}
    Greg Wilson, \& al. (2014): Best Practices for Scientific Computing, \textit{PLOS Biology}.\nocite{Wilson.2014}
    \end{center}
\end{frame}

\begin{frame}
\begin{cenumerate*}
\item Write programs for people, not computers.\vspace{0.3cm}
	\begin{itemize}
	\item A program should not require its readers to hold more than a handful of facts in memory at once.\vspace{0.2cm}
	\item Make names consistent, distinctive, and meaningful.\vspace{0.2cm}
	\item Make code style and formatting consistent.
	\end{itemize}
\end{cenumerate*}
\end{frame}


\begin{frame}
\begin{cenumerate}
\item Let the computer do the work. \vspace{0.3cm}
	\begin{itemize}
	\item Make the computer repeat tasks.\vspace{0.2cm}
	\item Save recent commands in a file for re-use.\vspace{0.2cm}
	\item Use a build tool to automate workflows.
	\end{itemize}
\end{cenumerate}
\end{frame}

\begin{frame}
\begin{cenumerate}
\item  Make incremental changes.\vspace{0.3cm}
	\begin{itemize}
	\item Work in small steps with frequent feedback and course correction. \vspace{0.2cm}
	\item  Use a version control system.\vspace{0.2cm}
	\item  Put everything that has been created manually in version control.
	\end{itemize}
\end{cenumerate}
\end{frame}

\begin{frame}
\begin{cenumerate}
\item Don't repeat yourself (or others).  \vspace{0.3cm}
	\begin{itemize}
	\item Every piece of data must have a single authoritative representation in the system. \vspace{0.2cm}
	\item  Modularize code rather than copying and pasting.\vspace{0.2cm}
	\item  Re-use code instead of rewriting it.
	\end{itemize}
\end{cenumerate}
\end{frame}

\begin{frame}
\begin{cenumerate}
\item  Plan for mistakes. \vspace{0.3cm}
	\begin{itemize}
	\item  Add assertions to programs to check their operation.\vspace{0.2cm}
	\item Use an off-the-shelf unit testing library.\vspace{0.2cm}
	\item  Turn bugs into test cases.\vspace{0.2cm}
	\item  Use a symbolic debugger.
	\end{itemize}
\end{cenumerate}
\end{frame}

\begin{frame}
\begin{cenumerate}
\item  Optimize software only after it works correctly. \vspace{0.3cm}
	\begin{itemize}
	\item  Use a profiler to identify bottlenecks.\vspace{0.2cm}
	\item  Write code in the highest-level language possible.
	\end{itemize}
\end{cenumerate}
\end{frame}

\begin{frame}
\begin{cenumerate}
\item  Document design and purpose, not mechanics. \vspace{0.3cm}
	\begin{itemize}
	\item  Document interfaces and reasons, not implementations.\vspace{0.2cm}
	\item  Refactor code in preference to explaining how it works.\vspace{0.2cm}
	\item  Embed the documentation for a piece of software in that software.
	\end{itemize}
\end{cenumerate}
\end{frame}

\begin{frame}
\begin{cenumerate}
\item  Collaborate. \vspace{0.3cm}
	\begin{itemize}
	\item  Use pre-merge code reviews.\vspace{0.2cm}
	\item  Use pair programming when bringing someone new up to speed and when tackling particularly tricky problems.\vspace{0.2cm}
	\item  Use an issue tracking tool.
	\end{itemize}
\end{cenumerate}
\end{frame}
